abc

### 2024-07-09 index.qmd
latest

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

@@

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
library(ggplot2)
library(combinat)
library(plotly)
library(htmltools)
library(broom)
```

```{webr-r}
dfl <- ManifoldDestinyWASMD::yout
df <- dplyr::select(dfl[[1]],S,T,U,V)
```

```{webr-r}
df
```

```{webr-r}
ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
ad
```

>>>>

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom'] 
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

@@

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
dfl <- ManifoldDestinyWASMD::yout
df <- dplyr::select(dfl[[1]],S,T,U,V)
```

```{webr-r}
```

### 2024-07-09 randpython.qmd
abcran
latest

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

```{r}
# script/R/simulations.R
```

1.

```{webr-r}
fit = lm(mpg ~ am, data = mtcars)
summary(fit)
```

```{r,echo=F}
knitr::knit_exit()
```

@@

>>>>

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
webr:
  show-startup-message: false      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table']             # Pre-install dependencies
filters:
  - panelize
  - webr
  - pyodide
---

@@

**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
